---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# poolABC

<!-- badges: start -->

[![](https://zenodo.org/badge/DOI/10.5281/zenodo.7520303.svg)](https://doi.org/10.5281/zenodo.7520303)

<!-- badges: end -->

The goal of `poolABC` is to help users perform model choice and parameter inference using Pool-seq data integrated into an Approximate Bayesian Computation (ABC) framework. This package provides functions to simulate Pool-seq data under models of ecotype formation and to import Pool-seq data from real populations. Two ABC algorithms are implemented to perform parameter estimation and model selection using Pool-seq data. Cross-validation can also be performed to assess the accuracy of ABC estimates and calculate model misclassification.

## Installation

You can install the development version of poolABC from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("joao-mcarvalho/poolABC")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(poolABC)
## basic example code
```
